---
title: "R Markdown"
subtitle: "A Brief Introduction"
author: "Bradley Goodnight"
date: "April 5, 2019"
output:
  powerpoint_presentation:
    reference_doc: template.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What is R Markdown?

 - R Markdown is a format for writing reports in R
 - It is based on Markdown, a simple formatting syntax designed to produce human-readable code
 - R Markdown can be used to embed R code and results into slideshows, pdfs, html documents, Word files and more
 
# Getting Started with Markdown

 - In RStudio Go to File -> New File -> R Markdown
 - You can select your desired output format: Word, HTML, PDF
 - To learn syntax go to Help -> Cheatsheets -> R Markdown Reference Guide
 
# Why use R Markdown?

 - R Markdown allows you to embed R code directly into your documents
 - This improves reproducibility, can simplify updates, and can be used to produce automated reports
 
# Example Use Cases

 - Embed R Code and results into documents
 - Change from one format to another (e.g. Powerpoint to Word)
 - Update or modify tables and graphs
 - Create automated reports
 
# Embeding R Code

 - Use either inline code or code "chunks"
 - Example of inline code: `r Sys.time()`
 - Example of code chunk:
```{r chunk}
# Example code chunk
Sys.time()
```
 
# Changing Formats

 - Ex: Convert Powerpoint slides to a Word document
 - Edit the output command at the top of the code **OR**
 - Click the arrow next to Knit and select a new format
 
# Updating Reports
```{r update, echo=FALSE}
# Create example data
Data <- c(1, 3, 6, 4, 9)

# Graph vector using points overlayed by a line 
plot(Data, type="o", col="blue")
```

# Automated Reports

 - Requires two files: a Markdown template and a loop script
 - Can create multiple versions of the same report with different inputs for each version
